Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-07-27 edubots_surveys.Rnw
clarifies on teachers not being part of student chat groups

As it can be seen by the answer to the first and last question, in general teachers do not want to participate in a chat group with students; either they want to simply leave the students alone in their own chat group, or otherwise they prefer not to be part of that interaction. In general, that is going to be the case no matter what; it is well known that students organize their own chat groups with many (and not always conveyable) intentions, so teachers do not want to take any part in it. Overwhelmingly, they don't want to participate in any chat group with students, but even less so if it includes the rest of the faculty.

>>>>

As it can be seen by the answer to the first and last question, in general teachers do not want to participate in a chat group with students; either they want to simply leave the students alone in their own chat group, or otherwise they prefer not to be part of that interaction. In general, that is going to be the case no matter what; it is well known that students organize their own chat groups with many (and not always conveyable) intentions, so teachers do not want to take any part in these informal or non institutionally-supported chat groups. Overwhelmingly, they do not want to participate in these kind of chat groups with students, but even less so if it includes the rest of the faculty.
